Flatiron cleaning

### 2021-12-17 Rmd/rdi analysis.Rmd
Modify imputation

>>>>

# Imputation for stagecat and debulking status

https://bookdown.org/mwheymans/bookmi/data-analysis-after-multiple-imputation.html#data-analysis-in-spss
https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf

Select the variables that may be important for predicting stagecat and debulking status:  
patientid, month_at_os, vitalstatus, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, therapy.  
Look at the Cox regression model before imputation.
```{r}
data <- Frontline %>% select(patientid, month_at_os, vitalstatus, 
                                 raceeth, diagnosisdate, surgerydate,
                                 ageatdx, stagecat, debulking, histology,
                                 therapy)
nonimp_cox_model <-
  coxph(Surv(month_at_os, vitalstatus) ~ raceeth + ageatdx + stagecat + debulking + histology + therapy,
        data = data)
nonimp_cox_model

Hazard <- nelsonaalen(data, month_at_os, vitalstatus)
dataset <- data.frame(data, Hazard)
```

Start imputation to look at matrix
```{r}
Cox.imp <- mice(dataset, m=1, maxit=0, seed=2795, printFlag=F)
# summary(Cox.imp)
Pred <- Cox.imp$predictorMatrix
# Pred["debulking", "month_at_os"] <- 0
Pred
```

Humm  
patientid is not used which is good. But therapy is not. -> fix that
```{r}
Pred[, "therapy"] <- 1
Pred["therapy", "therapy"] <- 0
Pred
```

Imputation and cox regression model on imputed data using the new predictor matrix.
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os, vitalstatus) ~ raceeth + ageatdx + stagecat + debulking + histology + therapy
       ))
pool(check1)$pooled
```

Do m = 36
```{r}
Cox.imp <- mice(dataset, m=36, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os, vitalstatus) ~ raceeth + ageatdx + stagecat + debulking + histology + therapy
       ))

summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
Results is exponentiated.

Complete the data and merge with original
```{r}
imputed_data <- complete(Cox.imp, include = FALSE) %>% 
  rename(imp_stagecat = stagecat, imp_debulking = debulking)

Frontline <- 
  full_join(Frontline, imputed_data %>% 
              select(patientid, starts_with("imp_")), 
            by = "patientid") 
Frontline_adjusted <- 
  full_join(Frontline_adjusted, imputed_data %>% 
              select(patientid, starts_with("imp_")), 
            by = "patientid") 
```
